---
title: "Weight of Fish"
author: "Shaun Ikeuchi"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

#Load Fish CSV
```{r}
fishdata <- read.csv("Fish.csv")
unique(fishdata$Species)
```


## Perch
```{r}

perchFish <- filter(fishdata, Species=="Perch")
perchFish <- perchFish %>%
  select(-Species)

```

### Best Models
We find best models for all three species. 


### Best Two regressor model
```{r}
perchModel <- lm(Weight~., data=perchFish)
summary(perchModel)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = perchFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

  
##Which is best??  

```{r}
which.max(summary.out$adjr2)
```

The best two parameters to predict weight is height and width.
```{r}
summary.out$which[3,]
```

```{r}
best2.model <- lm(Weight~Height+Width,data=perchFish)
summary(best2.model)
```

```{r}
anova(perchModel,best2.model)
```
## Pike
```{r}

pikeFish <- filter(fishdata, Species=="Pike")
pikeFish <- pikeFish %>%
  select(-Species)

```
### Best Models
```{r}
pikeModel <- lm(Weight~., data=pikeFish)
summary(pikeModel)
```
### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = pikeFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

```{r}
best2.model <- lm(Weight~Length1+Length3,data=pikeFish)
summary(best2.model)
```

The best two parameters to predict weight in a pike Fish is l1 and l3.

```{r}
anova(pikeModel,best2.model)
```
## Roach
```{r}

roachFish <- filter(fishdata, Species=="Roach")
roachFish <- roachFish %>%
  select(-Species)

```
### Best Models
```{r}
roachModel <- lm(Weight~., data=roachFish)
summary(roachModel)
```

### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = roachFish,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
```{r}
best2.model <- lm(Weight~Length3+Width,data=roachFish)
summary(best2.model)
```
```{r}
anova(roachModel,best2.model)
```
```{r}
which.max(summary.out$adjr2)
```
The best two parameters to predict weight is L3 and Width.

## Final Summary Statements


The best two parameters to predict weight in a perch fish is height and width.
The best two parameters to predict weight in a pike fish is l1 and l3.
The best two parameters to predict weight in a roach fish is l3 and width.


